Irt plot extra

### 2022-02-22 manuscript.Rmd
Table 4 updated

apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
```

>>>>

apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading > .30 is reported", font_size = "small")
```
